The role of lithic bipolar technology in Western Iberia’s Upper Paleolithic: the case of Vale Boi (southern Portugal)

### 2018-12-03 analysis/paper/paper.Rmd
small changes in load.libraries function

#Please see the functions.R file in /R directory for other libraries used for this compendium

library(knitr)
library(citr)
library(tidyverse)
library(broom)
library(FactoMineR)
library(factoextra)
library(ggpubr)
library(ggplot2)
library(ggrepel)
library(maptools)
library(ggmap)
library(devtools)
library(legendMap)
library(tab)
library(sjstats)
library(powerAnalysis)
library(epitools)
library(wesanderson)
library(ScaledPiecesVB)

>>>>

library(ScaledPiecesVB)

load.packages()
